\begin{thebibliography}{9}
\bibitem{main} 
Shokoohi-Yekta, Chen, Bilson, Bing Hu, Zakaria and Eamonn Keogh. University of California, Riverside. \textit{"Discovery of Meaningful Rules in Time Series".} KDD 2015, Proceedings of the 21th ACM SIGKDD. International Conference on Knowledge Discovery and Data Mining. Pages 1085-1094.

\bibitem{montgomeryx} 
D. C. Montgomeryx.
\textit{"Guidelines for designing experiments, design and analysis of experiments."} 5th Edition, 2000, pp. 13-17".

\bibitem{designexp} 
R. L. Mason. \textit{"Statistical Design and Analysis of Experiments With Applications to Engineering and Science."} Second Edition. John Wiley \& Sons. 2003.

\bibitem{multidimensional}
M. Vlachos, G. Kollios, and D. Gunopulos. \textit{"Discovering similar multidimensional trajectories."} Proc 18th Int. Conf. Data Eng. pp. 673–684, 2002.

\bibitem{keogh}
S. Chu, E. Keogh, and D. Hart, \textit{"Iterative Deepening Dynamic Time Warping for Time Series"}. pp. 195–212, 2002.

\bibitem{DTWcubicsplineinterpolation} 
H. Li, X. Wan, Y. Liang, and S. Gao. \textit{"Dynamic Time Warping Based on Cubic Spline Interpolation for Time Series Data Mining."} 2014 IEEE Int. Conf. Data Min. Work., pp. 19–26, 2014.

\bibitem{timewarping}
C. Ratanamahatana and E. Keogh, \textit{"Everything you know about dynamic time warping is wrong."} Third Work. Min. Temporal Seq. Data, pp. 22–25, 2004.

\bibitem{indexing} 
G. Al-Naymat, S. Chawla, and J. Taheri. \textit{"SparseDTW: A novel approach to speed up dynamic time warping."} Conf. Res. Pract. Inf. Technol. Ser., vol. 101, no. December 2003, pp. 117–127, 2009.

\bibitem{distancecomparison} 
H. Ding, G. Trajcevski, and P. Scheuermann, \textit{"Querying and mining of time series data: experimental comparison of representations and distance measures."} Proc. VLDB Endow., vol. 1, no. 2, pp. 1542–1552, 2008.

\bibitem{motifs} 
A. Mueen, E. Keogh, Q. Zhu, S. Cash, and B. Westover, \textit{"Exact Discovery of Time Series Motifs"}. Proc. 2009 SIAM Int. Conf. Data Min., pp. 473–484, 2009.

\bibitem{patterns} 
A. M. Denton, C. A. Besemann, and D. H. Dorr, \textit{"Pattern-based time-series subsequence clustering using radial distribution functions."} Knowl. Inf. Syst. Vol. 18, no. 1, pp. 1–27, 2009.

\bibitem{noise}
J. Hu, J. B. Gao, and K. D. White, \textit{"Estimating measurement noise in a time series by exploiting nonstationarity."} vol. 22, pp. 807–819, 2004.

\bibitem{rulediscovery}
G. Das, K. Lin, H. Mannila, G. Renganathan, and P. Smyth. \textit{"Rule discovery from time series."} Knowl. Discov. Data Min, pp. 16–22, 1998.

\bibitem{timewarping}
G. Al-Naymat, S. Chawla, and J. Taheri. \textit{"SparseDTW: A novel approach to speed up dynamic time warping."} Conf. Res. Pract. Inf. Technol. Ser., vol. 101, no. December 2003, pp. 117–127, 2009.

\bibitem{timewarpingindexing}
E. Keogh, Exact indexing of dynamic time warping, in: Processings of the 28th VLDB Conference, 2005, pp.358-380.

\bibitem{measurements}
Michael Morse, Jignesh M. Patel, \textit{"An Efficient and Accurate Method for Evaluating Time Series Similarity". University of Michigan}

\bibitem{elasticrules}
Park, S and Chu, S.W. Discovering and Matching Elastic Rules from Sequence Databases. Fundam. Inform. 47, 2001.

\bibitem{subsequencematching}
Wu, H., Salzberg, B., and Zhang, D., Online Event-driven Subsequence Matching over Financial Data Streams, SIGMOD Conference, 2004: 23-34.

\bibitem{robotics}
Gribovskaya, E., Kheddar, A., and Billard, A. Motion Learning and Adaptive Impedance for Robot Control during Physical Interaction with Humans. ICRA 2011.

\bibitem{weatherforcasting}
Brotzge, J. and Erickson, S., Tornadoes without NWS warning. Weather Forecasting, 25, 159-172. 2010.

\bibitem{weatherprediction}
McGovern, et al. Identifying Predictive Multi-Dimensional Time Series Motifs: An application to severe weather prediction. Data Mining and Knowledge Discovery. 2010.

\bibitem{type}
Li, G, Ji, S., Li, C, and Feng, J. Efficient type-ahead search on relational data: a TASTIER approach. SIGMOD Conference 2009: 695-706.

\bibitem{medical}
Weiss, S, Indurkhya, N, and Apte, C. Predictive Rule Discovery from Electronic Health Records. ACM IHI, 2010.

\bibitem{sigmod}
Eamonn Keogh, Shruti Kasetty, University of California, Riverside. On the Need for Time Series Data Mining Benchmarks: A Survey and Empirical Demonstration.

\bibitem{tak-chung}
Tak-chung Fu, A review on time series data mining, Department of Computing, Hong Kong Polytechnic University, Hunghom, Kowloon, Hong Kong, 2010.

\bibitem{kruskwal}
Yvonne Chan, Roy P Walmsley. Learning and Understanding the Kruskal-Wallis One-Way Analysis-of-Variance-by-Ranks Test for Differences Among Three or More Independent Groups. Published on December 1997.

\bibitem{concepts}
Carmelo Cassisi, Placido Montalto, Marco Aliotta, Andrea Cannata and Alfredo Pulvirenti. Similarity Measures
and Dimensionality Reduction Techniques for Time Series Data Mining. 2012 Cassisi et al.

\bibitem{datamining}
Han and Kamber (2005). Data Mining: Concepts and Techniques. Morgan Kaufmann
Publishers, CA.

\bibitem{algoanalysis}
Rakthanmanon, T., Campana, B., Mueen, A., Batista, G., Westover, B., Zhu, Q., Zakaria, J., and Keogh, E. (2012). Searching and mining trillions of time series subsequences under 54 dynamic time warping. In Proceedings of the 18th ACM SIG KDD international conferenceon Knowledge discovery and data mining, pages 262-270. ACM.

\bibitem{euclidean}
Gustavo Batista, Xiaoyue Wang, Eamonn J. Keogh, A Complexity-Invariant Distance Measure for Time Series, University of California, Riverside, University of Sao Paulo - USP.

\bibitem{swale}
Michael Morse, Jignesh Patel. An Efficient and Accurate Method for Evaluating Time Series Similarity. University of Michigan. SIGMOD’07, June 11–14, 2007, Beijing, China.

\bibitem{dtw}
D. Berndt, J. Clifford. Using Dynamic Time Warping to Find Patterns in Time Series. In AAAI-94 Workshop on Knowledge Discovery in Databases, pages 359–370, 1994.

\bibitem{timeseriesapplications}
Robert Shumway, David Stoffer. Time Series Analysis and Its Applications - With R Examples. Third edition. Pages 1-7. 2011.

\bibitem{dataminingtimeseries}
Chotirat Ann Ratanamahatana, Jessica Lin, Dimitrios Gunopulos, Eamonn Keogh. Mining Time Series Data. University of California, Riverside. 2014.

\bibitem{spade}
Yueguo Chen Mario A, Nascimento Beng Chin Ooi, Anthony K. H. Tung. National University of Singapore. University of Alberta. On Shape-based Pattern Detection in Streaming Time Series.
\end{thebibliography}